\documentclass[10pt]{book}

\usepackage{luatexja-fontspec}
%\setmainjfont{MS Mincho} % \mcfamily
%\setsansjfont{MS Gothic} % \gtfamily
\usepackage{fontspec}
\usepackage{fullpage} % to reduce the margins
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{paracol}
\usepackage{lettrine}

\setmainfont{Gentium Plus}
\usepackage[japanese,english]{babel}
\newcommand{\switchjapanese}[1][]{\selectlanguage{japanese} \switchcolumn*[#1]}
\newcommand{\switchenglish}{\selectlanguage{english} \switchcolumn}

% Roles
\newcommand{\role}[1]{\textbf{#1}}
\newcommand{\roleBarretEng}{\role{Barret}}
\newcommand{\roleBarretJap}{\role{バレット}}
\newcommand{\roleBiggsEng}{\role{Biggs}}
\newcommand{\roleBiggsJap}{\role{ビッグス}}
\newcommand{\roleJessieEng}{\role{Jessie}}
\newcommand{\roleJessieJap}{\role{ジェシー}}
\newcommand{\roleCloudEng}{\role{Cloud}}
\newcommand{\roleCloudJap}{\role{クラウド}}
\newcommand{\stageDirection}[1]{\textit{#1}}
\newenvironment{paracolSection}
    {\begin{paracol}{2}
    \selectlanguage{japanese}
    }
    {
    \end{paracol}
    }

% RED
\definecolor{benred8}{HTML}{E82C00} 

% BLUE
\definecolor{benblue1}{HTML}{2B22C7}

% YELLOWS
\definecolor{benyellow1}{HTML}{FFD435}
\definecolor{benyellow2}{HTML}{7C6F3B}

% Luke Smith's title formatting
\titleformat{\section}
{\scshape\centering\Large}
{§\thesection}
{1em}
{}
\titleformat{\subsection}
{\scshape\centering\large}
{§\thesubsection}
{1em}
{}
\titleformat{\subsubsection}
{\itshape\centering\large}
{§\thesubsubsection}
{1em}
{}

\title{Final Fantasy VII Bilingual Script\\ファイナルファンタジーVII英和セリフ}
\author{Kazushige Nojima・野島一成\\Yoshinori Kitase・北瀬佳範\\Hironobu Sakaguchi・坂口博信\\Tetsuya Nomura・野村哲也}

\begin{document}

\maketitle

\section*{Disc 1}

\stageDirection{The opening sequence: A whirl of stars, humming softly, the view slowly
drifting downwards and changing to show Aeris's face lit by Mako. She stands
and walks out into the streets of Midgar as the camera pans back to show the
city in full before again diving in, this time following a train as it pulls
into a station in Sector 8. Biggs and Jessie leap off first, taking out the two
guards stationed there. Wedge follows, and the three of them run ahead. Barret
and Cloud leap down last.}

\begin{paracolSection}

\roleBarretJap

行くぞ、新入り！ オレに続け！

\switchenglish

\roleBarretEng

C'mon newcomer. Follow me.

\end{paracolSection}

\stageDirection{Barret runs ahead. Cloud follows, taking out two guards who stand in his path.
He joins Biggs, Wedge, and Jessie at the gate to the reactor complex, where
Jessie is working to open the door.}

\begin{paracolSection}

\roleBiggsJap

さすが、ソルジャー！ でもよ、反神羅（しんら）グループ【アパランチ】にソルジャーが参加するなんてスゲェよな！

\switchenglish

\roleBiggsEng

Wow! You used to be in SOLDIER all right! ...Not everyday ya find one in a group like AVALANCHE.

\switchjapanese

\roleJessieJap

その話って本当だったの？ ソルジャーって言ったら 私たちの敵でしょ？

どうして、そのソルジャーが私たちアバランチに協力するわけ？

\switchenglish

\roleJessieEng

SOLDIER? Aren't they the enemy?

What's he doing with us in AVALANCHE?

\switchjapanese

\roleBiggsJap

早とちりするな、ジェシー。元、ソルジャーなんだってさ

今はもう神羅（しんら）をやめちまって 俺たちの仲間ってわけさ

まだ名前聞いてなかったよな。教えてくれ

\switchenglish

\roleBiggsEng

Hold it, Jessie. He WAS in SOLDIER.

He quit them and now is one of us.

Didn't catch your name...

\switchjapanese

\roleCloudJap

……クラウドだ

\switchenglish

\roleCloudEng

...Cloud.

\end{paracolSection}

\end{document}

